On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-09-13 Manuscript/manuscript.tex
Fixed order of last paragraph

Figure~\ref{fig:RankScatterplots} shows the data that is being analyzed
with the rank-based methods.  In each of the three graphs, athletes who competed
in the 2022 finals are having their times compared to another event they competed
at.  It is worth noting that each instance of the 2022 data is different, because
those who competed at both the 2019 and 2022 World Championships will be
different athletes than those who competed at both the 2022 and 2023 World
Championships. This data was only for athletes who competed
in at least one race at each championship, however it is possible for athletes
to have competed in one race in 2019 and two races in 2022.  The 2022 World
Championship Heats and Semifinals both had on average lower reaction times than
their respective 2019 races, and the 2022 finals were substantially faster. It
is also worth noting is that the fastest reaction time in the 2022 Finals and 2022
Semifinals both came from Devon Allen, but the difference between 0.101 and 0.099
seconds was the difference in what caused him to be disqualified. 
\eds{Please reorganize the labels so they are either in one of the following 
orders:
2019 Heat, 2019 Semi, 2019 final, 2022 Heat, 2022 Semi, 2022 final  OR
2019 Heat, 2022 Heat, 2019 Semi, 2022 Semi, 2019 final, 2022 final.  
(I am not sure which is better, but perhaps the latter?)}
of{I re-worked this graph completely, please let me know what you think.  For
each graph I currently list them in chronological order: so 2022 then 2023 but
I list 2022 second when comparing it to 2019/rank comparison.  Please let me
know your thoughts on this and if I should list 2022 and then 2023 for visual
consistency.}

@@

This paper has shown that a reaction time of 0.1 seconds is not as extreme as
one may think, and that based on the probabilities in table~\ref{tab:Sim_time},
World Athletics should consider changing the disqualification barrier to 0.8
seconds.  If they were to do so, they would allow athletes like Allen to be able
to react faster without fear of being disqualified.  The second part of this
paper showed that athletes' reaction times at the 2022 World Track and Field
Championships were generally faster than their reaction times at other
competitions. Table~\ref{tab:Clusrankresults} shows multiple significant p values
that indicate differences in average reaction times for athletes who competed at
the 2022 World Track and Field Championship and another competition.  Taken
together, the results show that 2022 was an outlier and despite being disqualified,
Allen's time was not so extreme.

>>>>

Figure~\ref{fig:RankScatterplots} shows the data that is being analyzed
with the rank-based methods.  In each of the three graphs, athletes who competed
in the 2022 finals are having their times compared to another event they competed
at.  It is worth noting that each instance of the 2022 data is different, because
those who competed at both the 2019 and 2022 World Championships will be
different athletes than those who competed at both the 2022 and 2023 World
Championships. This data was only for athletes who competed
in at least one race at each championship, however it is possible for athletes
to have competed in one race in 2019 and two races in 2022.  The 2022 World
Championship Heats and Semifinals both had on average lower reaction times than
their respective 2019 races, and the 2022 finals were substantially faster. It
is also worth noting is that the fastest reaction time in the 2022 Finals and 2022
Semifinals both came from Devon Allen, but the difference between 0.101 and 0.099
seconds was the difference in what caused him to be disqualified. 
\eds{Please reorganize the labels so they are either in one of the following 
orders:
2019 Heat, 2019 Semi, 2019 final, 2022 Heat, 2022 Semi, 2022 final  OR
2019 Heat, 2022 Heat, 2019 Semi, 2022 Semi, 2019 final, 2022 final.  
(I am not sure which is better, but perhaps the latter?)}
\of{I re-worked this graph completely, please let me know what you think.  For
each graph I currently list them in chronological order: so 2022 then 2023 but
I list 2022 second when comparing it to 2019/rank comparison.  Please let me
know your thoughts on this and if I should list 2022 and then 2023 for visual
consistency.}

@@

The first part of this paper showed that athletes' reaction times at the 2022 
World Track and Field Championships were generally faster than their reaction 
times at other competitions. Table~\ref{tab:Clusrankresults} shows multiple 
significant p values that indicate differences in average reaction times for 
athletes who competed at the 2022 World Track and Field Championship and another
competition.  Additionally, this paper has shown that a reaction time of 0.1 
seconds is not as extreme as one may think, and that based on the probabilities
in table~\ref{tab:Sim_time}, World Athletics should consider changing the 
disqualification barrier to 0.8 seconds.  If they were to do so, they would 
allow athletes like Allen to be able to react faster without fear of being 
disqualified.  Taken together, the results show that 2022 was an outlier and 
despite being disqualified, Allen's time was not so extreme.
